Parameter Space Representation of Pareto Front to Explore Hardware-Software Dependencies

### 2014-07-31 paper.tex
AA: ho letto i numerical results

In this work we present PS, a new multiobjective exploration
algorithm. The basic idea is to recognize \emph{interesting} regions, i.e.
regions of the configuration space that are proving to provide better
configurations with regard to other ones. PS evaluates more configurations in
interesting regions while exploring less thoroughly the rest of the
configuration space. After a detailed formal description of the
algorithm and the underlying concepts, we show a 
case study involving the hardware/software exploration of a VLIW
architcture. Qualitative and quantitative comparisons of PS
against a well-know multiobjective genetic approach demonstrate that,
while not outperforming it in terms of dominance, the proposed
approach can trade the uniformity and granularity qualities of the
solutions found for obtaining larger Pareto sets, thus representing a
further choice for designer when objective constrains allow it.
\end{abstract}

@@

\section{Conclusions}
In this work we presented a multiobjective strategy which 
introduces the concept of Parameter Space representation of Pareto
Front. A case study of a VLIW architecture involving strong
hardware/software dependencies has been carried out to evaluate
effectiveness with different amount of simulations budget.
A qualitative/quantitative comparison against a widespread multiobjective genetic
approach showed how the proposed strategy can result in a different
distribution of Pareto points which trades solutions granularity with
improved pareto extension.

>>>>

In this work we present PS, a new multiobjective exploration
algorithm. The basic idea is to recognize \emph{interesting} regions, i.e.
regions of the configuration space that are proving to provide better
configurations with regard to other ones. PS evaluates more configurations in
interesting regions while exploring less thoroughly the rest of the
configuration space. After a detailed formal description of the
algorithm and the underlying concepts, we show a 
case study involving the hardware/software exploration of a VLIW
architecture. Qualitative and quantitative comparisons of PS
against a well-know multiobjective genetic approach demonstrate that,
while not outperforming it in terms of dominance, the proposed
approach can trade the uniformity and granularity qualities of the
solutions found for obtaining larger Pareto sets, thus representing a
further choice for designer when objective constrains allow it.
\end{abstract}

@@

\section{Conclusions}
In this work we presented PS, a multiobjective strategy which 
introduces the concept of Parameter Space representation of Pareto
Front. A case study of a VLIW architecture involving strong
hardware/software dependencies has been analyzed \comment{AA: da ``carried out'' a ``analyzed'', carry out a case study (effettuare un caso studio) mi suonava strano } carried out to evaluate
effectiveness with different amount of simulations budget.
A qualitative/quantitative comparison against a widespread multiobjective genetic
approach showed how the proposed strategy can result in a different
distribution of Pareto points which trades solutions granularity with
improved Pareto extension.
